PM Mungbean meta-analysis

### 2020-06-11 02_Preliminary_analysis.Rmd
Corrections and removing irrelevant lines

## Explore and Visualise Data
First lets import the data. Each row provides the mean yield for each experimental treatment.
```{r echo=FALSE, message=FALSE, warning=FALSE, include= FALSE}
# Import data
PM_MB_means <- import_data() 
```

@@

Now we have calculated proportional yield gains we can inpect the difference between the fungicide active ingredients

```{r Fungicide_x_nSprays_tble2, message=FALSE}
PM_MB_means %>%
   group_by(fungicide_ai, total_fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain.",
         col.names = c("Fungicide active ingredient", "Total fungicide applications","n Treatments"," 2.5% quartile","Median proportional grain yield", "Mean proportional grain yield","97.5 % quartile")) %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   footnote(general = "Fungicides with less than five observations were omitted from this table")

@@

There is a small yield effect among the strobilurin fungicide mixes and the DMI fungicides. 
The follow up spray seems to show an increase in yield protection.
Interestingly sulphur sprays show good protection when sprayed twice.

@@

There is a large amount of variation in the propiconazole dose, let's inspect the difference in yields for each dose.

```{r PropiDoseEffect}
PM_MB_means %>%
   filter(fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = prop_YG)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Yield for each respective propiconazole dose, faceted by number of applications") +
   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
   facet_grid(cols = vars(total_fungicide))

@@

This table shows that the majority of treatments inspected one and two spray manangement practices.

@@

YV1[[3]]
```
This plot shows a large amount of yield volatility in all cultivars except green diamond. Green Diamond shows little volatility probably because this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trials.

Now let's look at overall yields for each cultivar, where trial is not a factor, in only the no spray treatments.

@@

Volatility of the cultivars are less, albeit fairly similar, when trial is not considered as a factor (when we inspect plots of all treatments).

@@

PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
          row_spacing == 0.75) %>%
   glimpse()
```

@@

```{r rainLMrsquared}
ggplot(lm_rain, aes(x = start_day, y = end_day, z = lm_rsquared)) +
   geom_raster(aes(fill = lm_rsquared), interpolate = TRUE) +
   geom_contour(bins = 15, colour = "white") +
   geom_point(data = lm_rain[which(lm_rain$lm_rsquared == max(lm_rain$lm_rsquared)), ],
              aes(x = start_day, y = end_day),
              colour = " red") +
   scale_fill_distiller(palette = "RdBu") 
```

@@

season_dates[c(1:2,6), "Planting_day"] <- 1
#  yday(as.Date("2012-02-28") - 7) # Correct dplanted in december and emerged in February, Assuming due to lack of rain or recording error. Using 7 days prior to emergence day as planting day

@@

#### Effect of Fungicide

**Fungicide effect on proportional yield gain with respect to time of application**  
First let's look at the quantiles for each fungicide irrespective of other factors.
We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.

```{r fungicide_proportion_yield}
# plot table as a box plot
PM_MB_means %>%
   filter(
      fungicide_ai == c(
         "200 g/L tebuconazole + 120 g/L azoxystrobin" ,
         "200 g/L azoxystrobin + 80 g/L cyproconazole",
         "tebuconazole",
         "propiconazole",
         "sulphur"
      ),
      total_fungicide != 3
   ) %>%
   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
   geom_boxplot(aes(fill = fungicide_ai)) +
   geom_hline(aes(yintercept = 0), size = 0.5, colour = "red") +
   labs(x = "Proportion of grain yield saved",
        title = "Grain yield proportion saved,\ngrouped by fungicide type") +
   theme(
      panel.grid.major = element_line(colour = "grey80"),
      panel.grid.minor = element_line(colour = "grey50"),
      panel.background = element_rect(fill = NA)
   ) +
   guides(fill = guide_legend(title = "Fungicide")) +
   scale_fill_usq() +
   facet_grid(rows = vars(total_fungicide))+
   coord_flip()

While there is some differences in the variation between tebuconazole and propiconazole, the medians are very similar. 
I think it is safe to combine these fungicides, with the same mode of action in the meta-analysis.

We need to also define the relationship between yield loss and disease severity.
When exploring this data we should look primarily at the no spray control plots

```{r yield_x_PMseverity}
PM_MB_means %>%
   filter(fungicide_ai == "control") %>%
   ggplot(aes(x = PM_final_severity, y = grain_yield.t.ha.)) +
   geom_point() +
   geom_smooth(method = "lm")
```

From the data that we have, it is difficult to determine if there is an association between powdery mildew severity and grain yield in no spray control plots.

>>>>

## Explore and Visualise Data
First lets import the data. Each row provides the mean yield for each experimental treatment.
```{r echo=TRUE, message=FALSE, warning=FALSE}
# Import data
PM_MB_means <- import_data() 
```

@@

Now we have calculated proportional yield gains we can inspect the difference between the fungicide active ingredients

```{r Fungicide_x_nSprays_tble2, message=FALSE}
PM_MB_means %>%
   group_by(fungicide_ai, total_fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain.",
         col.names = c("Fungicide active ingredient", "Total fungicide applications","n Treatments"," 2.5% quartile","Median proportional grain yield", "Mean proportional grain yield","97.5 % quartile"),
         align = "c") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   column_spec(c(2,3), width = "1cm") %>% 
   footnote(general = "Fungicides with less than five observations were omitted from this table")

@@

There is a small yield effect among the strobilurin fungicide mixes and the DMI fungicides. 
While there is some differences in the variation between tebuconazole and propiconazole, the medians are very similar. 
I think it is safe to combine these fungicides, with the same mode of action in the meta-analysis.
The follow up spray seems to show an increase in yield protection.
Interestingly sulphur sprays show good protection when sprayed twice.

@@

Doses for propiconazole range from 62.5 to 125, a large variation.
Let's inspect the difference in yields for each dose.

```{r PropiDoseEffect}
PM_MB_means %>%
   filter(fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = relevel(as.factor(dose_ai.ha), "62.5"), y = prop_YG)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Yield for each respective propiconazole dose,\nfaceted by number of applications") +
   geom_boxplot(fill = usq_cols("usq charcoal"), alpha = 0.5) +
   facet_grid(cols = vars(total_fungicide))

@@

This table shows that the majority of treatments inspected one and two spray management practices.

@@

YV1[[3]]
```
This plot shows a large amount of yield volatility in all cultivars except green diamond. Green Diamond shows little volatility probably because this cultivar is only featured in `r length(unique(PM_MB_means[PM_MB_means$host_genotype == "Green Diamond","trial_ref"]))` trial.

Now let's look at overall yields for each cultivar, where trial is not a factor, in only the no spray control treatments.

@@

Volatility of the cultivars are less, albeit fairly similar, in control plots when trial is not considered as a factor.

@@

@@

@@

season_dates[c(1:2,6), "Planting_day"] <- 1

@@
